|

### 2023-04-05 paper.Rmd
clear up language for NHST + vis inf

In practice, over-interpretation of a single plot is common.  For instance, in @roy_chowdhury_using_2015, some over-interpreted the separation between gene groups in a two-dimensional projection of a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups. To mitigate this over-interpretation, @buja_statistical_2009 proposed a line-up protocol to assess plots in a manner analogous to the null hypothesis significance testing framework. More specifically, the protocol consists of $m$ randomly placed plots, where one plot is the data plot, and the remaining $m - 1$ null plots have the identical graphical procedure except the data has been replaced with data consistent with $H_0$, that the model is correctly specified. Then, an observer who have not seen the data plot will be asked to point out the most different plot from the lineup. Under $H_0$, it is expected that the data plot would have no distinguishable difference from the null plots, and the probability that the observer correctly picks the data plot is $1/m$. If one rejects $H_0$ as the observer correctly picks the data plot, then the Type I error of this test is $1/m$.

>>>>

In practice, over-interpretation of a single plot is common.  For instance, in @roy_chowdhury_using_2015, some over-interpreted the separation between gene groups in a two-dimensional projection of a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups. To mitigate this over-interpretation, @buja_statistical_2009 proposed a line-up protocol to assess plots in a manner analogous to the null hypothesis significance testing (NHST) framework. More specifically, the protocol consists of $m$ randomly placed plots, where one plot is the data plot, and the remaining $m - 1$ plots, referred to as the _null plots_, have the identical graphical procedure as the data plot except the data is replaced with a data generation mechanism that is consistent with the null hypothesis, $H_0$. Then, an observer who have not seen the data plot will be asked to point out the most different plot from the lineup. Under $H_0$, it is expected that the data plot would have no distinguishable difference from the null plots, and the probability that the observer correctly picks the data plot is $1/m$. If one rejects $H_0$ as the observer correctly picks the data plot, then the Type I error of this test is $1/m$. This protocol requires apriori specification of $H_0$ (or at least a null data generating mechanism) much like the requirement of knowing the distribution of the test statistic in NHST.
